Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Saturn-Sized Planet in IC~2602

### 2020-07-10 paper/ms.tex
update manuscript

\edit1{Phil + Karen TODO: please correct as appropriate}
We scheduled the observations using {\bf \texttt{SOFTWARE}} (CITE).
The photometric data were calibrated and extracted using the
\texttt{AstroImageJ} software package
\citep{collins_astroimagej_2017}.  Comparison stars of similar
brightness were used to produce the final light curves, each of which
showed a roughly 4$\,$ppt dip near the expected transit time.

\paragraph{Custom aperture analysis}
Based solely on the TESS data, both Star A and Star B were possible
sources of blended eclipsing binary signals.  Star B is resolved in
the ground-based images; Star A is not.

@@

To assess the possibility that Star A is an eclipsing body, we created
light curves with a custom set of circular apertures with radii of
$2.1''$ and positions ranging from Star A (2.3$''$ west of \tn) to
2.3$''$ east of \tn.  We did not detect any variation of the transit
depth along this line of light curves. The apertures east of \tn\
exclude over 90\% of the flux from Star A.  The eclipse on Star A
would therefore need to have depth greater than unity to produce the
observed eclipse depth.  We take the lack of a transit depth variation
along these light curves as evidence that \tn\ is the source of the
transit signal to within $\approx2.0''$.  The lack of variation of
transit depth with aperture location is consistent with \tn\ being the
source of transits, because the uncertainty of the transit depth
measurements ($\approx 15\%$) is much greater than the maximum
dilution from Star A ($\approx 1\%$).

@@

\input{ic2602_ages.tex}

@@

% \clearpage
%\clearpage
\input{starparams.tex}
%\clearpage
\input{model_posterior_table.tex}
\clearpage
\input{TOI837_phot_table.tex}
\input{TOI837_rv_table.tex}
%\clearpage

>>>>

We scheduled our transit observations using the {\tt TESS Transit Finder}, which is a customized version
of the {\tt Tapir} software package \citep{Jensen:2013}.  The photometric data were calibrated and
extracted using \texttt{AstroImageJ} \citep{collins_astroimagej_2017}.
Comparison stars of similar brightness were used to produce the final
light curves, each of which showed a roughly 4$\,$ppt dip near the
expected transit time.  The data are reported in Table~\ref{tab:phot}
and plotted in Figure~\ref{fig:groundphot}.

\paragraph{Custom aperture analysis}
Based solely on the TESS data, both Star A and Star B were possible
sources of blended eclipsing binary signals.  Star B is resolved in
the 0.36m images; Star A is not.

@@

To assess the possibility that Star A is an eclipsing body, we created
light curves with a custom set of circular apertures with radii of
$2.1''$ and positions ranging from Star A (2.3$''$ west of \tn) to
2.3$''$ east of \tn.  We did not detect any variation of the transit
depth along this line of light curves. The apertures east of \tn\
exclude over 90\% of the flux from Star A.  The eclipse on Star A
would therefore need to have depth greater than unity to produce the
observed eclipse depth.  We therefore interpret the lack of asymmetry
between the western-most (centered on Star A) and eastern-most
(furthest from Star A) light curves as conclusive evidence that \tn\
is the source of the transit signal to within $\approx2.0''$. 
To verify self-consistency, we checked that the maximum dilution from Star A
($\approx 1\%$) is less than the uncertainty of the transit depth
measurements ($\approx 15\%$), and so the lack of variation of transit
depth with aperture location is consistent with \tn\ being the source
of transits.

@@

@@

% \clearpage
%\clearpage

\input{ic2602_ages.tex}
\input{starparams.tex}
%\clearpage
\input{model_posterior_table.tex}
\clearpage
\input{TOI837_phot_table.tex}
\input{TOI837_rv_table.tex}
%\clearpage
